---
output: pdf_document
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{multicol}
  - \usepackage{graphicx}
  - \graphicspath{ {.} }
geometry: margin = 0.25in
date: "`r Sys.Date()`"
params:
    report_header: page_header_list
    info_and_stats_viz: info_and_stats_list
    spray_and_advanced_viz: spray_and_advanced_list
    batter_heatmaps_viz: batter_heatmaps_list
---

```{r setup, fig.width=8.5, fig.height=11, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

\begin{multicols}{3} % Create a 3 column layout to hold the header logo, player name, and date range

\includegraphics[width=0.4\columnwidth]{ALPB_Logo} % include the ALPB logo

\hspace{0pt}
\vfill
\hspace{-0.5in}\large\textbf{`r paste0(params$report_header[[1]], " vs. RHP")`} % include the player name
\vfill
\hspace{0pt}

\hspace{0pt}
\vfill
\large\textbf{`r paste0(params$report_header[[2]], " to ", params$report_header[[3]])`} % include the date range
\vfill
\hspace{0pt}

\end{multicols}
\vspace{-0.35in}
\noindent\rule{\textwidth}{0.75pt} 

```{r fig.width=8.5, fig.height=1}
# chunk for the basic info and basic stats
params$info_and_stats_viz[[1]]
```

```{r fig.width=8.5, fig.height=3}
# chunk for the spray chart and advanced stats
params$spray_and_advanced_viz[[1]]
```

\begin{multicols}{3} % 3 column headers for the heatmaps



\hspace{0.2in}\centerline{\LARGE\textbf{EV > 95}}



\hspace{-0.05in}\centerline{\LARGE\textbf{Whiff}}



\hspace{-0.05in}\centerline{\LARGE\textbf{Chase}}
\end{multicols}

```{r fig.width=8.5, fig.height=5}
# chunk for the batter heatmap visual
params$batter_heatmaps_viz[[1]]
```

\newpage
\begin{multicols}{3}

\includegraphics[width=0.4\columnwidth]{ALPB_Logo}

\hspace{0pt}
\vfill
\hspace{-0.5in}\large\textbf{`r paste0(params$report_header[[1]], " vs. LHP")`}
\vfill
\hspace{0pt}

\hspace{0pt}
\vfill
\large\textbf{`r paste0(params$report_header[[2]], " to ", params$report_header[[3]])`}
\vfill
\hspace{0pt}

\end{multicols}
\vspace{-0.35in}
\noindent\rule{\textwidth}{0.75pt}

```{r fig.width=8.5, fig.height=1}
params$info_and_stats_viz[[2]]
```

```{r fig.width=8.5, fig.height=3}
params$spray_and_advanced_viz[[2]]
```

\begin{multicols}{3}



\hspace{0.2in}\centerline{\LARGE\textbf{EV > 95}}



\hspace{-0.05in}\centerline{\LARGE\textbf{Whiff}}



\hspace{-0.05in}\centerline{\LARGE\textbf{Chase}}
\end{multicols}

```{r fig.width=8.5, fig.height=5}
params$batter_heatmaps_viz[[2]]
```
